Brownian Dynein Model

### 2016-09-01 latex/paper.tex
Fix paper.tex changes.
Add minor changes to paper.tex.

@@

\section{Onebound}

\begin{figure}
  \includegraphics[width=\columnwidth]{../figures/code-onebound}
  \caption{Angles used in one-bound case.}\label{fig:onebound}
\end{figure}

First, some definitions...
\begin{align*}
F_{bmx} &= \frac{f_{bmx} + R_{bmx}}{\gamma}\\
F_{xt } &= \frac{f_{xt} + R_{xt}}{\gamma}\\
...\\
X_{bs} &= \frac{X_{bm} - X_{bb}}{\gamma}\\
X_{bt} &= \frac{X_t - X_{bm}}{\gamma}\\
...\\
\end{align*}

@@

\subsection{Expanded velocities}

\begin{align*}
\dot{X}_{bm} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb}\\
\dot{X}_{t } &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm}\\
\dot{X}_{um} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um}\\
\dot{X}_{ub} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub}\\
\end{align*}

>>>>

\newcommand{\gb}{\frac{1}{\gamma_b}}
\newcommand{\gm}{\frac{1}{\gamma_m}}
\newcommand{\gt}{\frac{1}{\gamma_t}}

@@

\section{Onebound derivation}

First, some definitions...
\begin{align*}
F_{bmx} &= \frac{f_{bmx} + R_{bmx}}{\gamma}\\
F_{xt } &= \frac{f_{xt} + R_{xt}}{\gamma}\\
..\\
\end{align*}

\begin{align*}
X_{bs} &= \frac{X_{bm} - X_{bb}}{\gamma}\\
X_{bt} &= \frac{X_{t} - X_{bm}}{\gamma}\\
X_{ut} &= \frac{X_{um} - X_{t}}{\gamma}\\
X_{us} &= \frac{X_{ub} - X_{um}}{\gamma}\\
\end{align*}

\begin{align*}
Y_{bs} &= \frac{Y_{bm} - Y_{bb}}{\gamma}\\
Y_{bt} &= \frac{Y_{t} - Y_{bm}}{\gamma}\\
Y_{ut} &= \frac{Y_{um} - Y_{t}}{\gamma}\\
Y_{us} &= \frac{Y_{ub} - Y_{um}}{\gamma}\\
\end{align*}

\subsection{Domain positions}
\begin{align*}
X_{bm} &= L_s\cos(\theta_{bb})\\
X_{t } &= L_s\cos(\theta_{bb}) + L_t\cos(\theta_{bm})\\
X_{um} &= L_s\cos(\theta_{bb}) + L_t\cos(\theta_{bm}) - L_t\cos(\theta_{um})\\
X_{ub} &= L_s\cos(\theta_{bb}) + L_t\cos(\theta_{bm}) - L_t\cos(\theta_{um}) - L_s\cos(\theta_{ub})\\
\end{align*}

\begin{align*}
Y_{bm} &= L_s\sin(\theta_{bb})\\
Y_{t } &= L_s\sin(\theta_{bb}) + L_t\sin(\theta_{bm})\\
Y_{um} &= L_s\sin(\theta_{bb}) + L_t\sin(\theta_{bm}) - L_t\sin(\theta_{um})\\
Y_{ub} &= L_s\sin(\theta_{bb}) + L_t\sin(\theta_{bm}) - L_t\sin(\theta_{um}) - L_s\sin(\theta_{ub})\\
\end{align*}

\subsection{Domain velocities}
\begin{align*}
\dot{X}_{bm} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb}\\
\dot{X}_{t } &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm}\\
\dot{X}_{um} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um}\\
\dot{X}_{ub} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub}\\
\end{align*}

@@
